How has the Amazon been construed as a problem? Preliminary Analysis

### 2022-03-30 analysis/analysis_livio.Rmd
#preliminary plots for text

ama_mx %>%
  count(year, mx_cat)%>%
  group_by(year) %>%
  mutate(perc=n / sum(n))  %>%
  ggplot(., aes(x=year, y=perc, fill=mx_cat))+
  geom_bar(stat="identity", position="dodge")+
  geom_smooth(color="black", size=.3, se= FALSE)+
  labs(
    x = "", y = "", title ="Plot 5: Problem-construction evolution in time",
    subtitle = "Sample composed by 2400 problem-constructions in 1885 Amazonian statements in presidential speeches since 1985",
    caption = "") +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "none"
  )+
  facet_wrap(~ mx_cat, ncol=3, scales="free_y")

>>>>

ama_mx %>%
  count(year, mx_cat)%>%
  group_by(year) %>%
  mutate(perc=n / sum(n))  %>%
  ggplot(., aes(x=year, y=perc, fill=mx_cat))+
  geom_bar(stat="identity", position="dodge")+
  geom_smooth(color="black", size=.3, se= FALSE)+
  labs(
    x = "", y = "", title ="Plot 5: Mixed-types evolution overtime",
    subtitle = "Sample composed by 2400 problem-constructions in 1885 Amazonian statements in presidential speeches since 1985",
    caption = "") +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "none"
  )+
  facet_wrap(~ mx_cat, ncol=2, scales="free_y")
